\section{Results for the complete graph}
We now turn our attention to the complete graph. As we discussed in the preliminaries in \Cref{subsec:search qw complete graph} and \Cref{subsec:local adiabatic}, with the complete graph we are able to solve the search problem using the standard time-independendent quantum walks Hamiltonian with time scaling of $O(\sqrt{N})$. Additionally for the unstructured search - which is equivalent to the complete graph - we showed that with the local adiabatic evolution we're able to get the same speedup of $O(\sqrt{N})$, while that was not the case for the global adiabatic evolution that had the same time scaling as the classical search. Although Wong proved that for the complete graph it is not possible to solve the search problem with an adiabatic quantum walk algorithm, for completeness we extend the time-dependent Hamiltonian implementation to the complete graph. Clearly we are not able to achieve any speedup nor necessarily any comparable time scaling, but we might get some interesting insights in terms of probability distribution and robustness.

    \subsection{Comments on the placement of $\gamma$}
    Firstly we recall that in \Cref{subsec:complete graph} we introduced the search hamiltonian as
    \begin{equation}
      H = \gamma L -\ket{w}\bra{w}
    \end{equation}
    We quickly notice that the $\gamma$ parameter is in front of the Laplacian, compared to the time-dependent Hamiltonian considered throughout our work where $\gamma$ was placed in front of the oracle $\ket{w}\bra{w}$. We could now proceed by comparing the time-independent and time-dependent approaches with the $\gamma$ placement as in literature - i.e. in front of the Laplacian - or as we did in \Cref{sec:time_dependent_hamiltonian}. In order to be consistent with the standard quantum walks search on the complete graph discussed in \Cref{subsec:search qw complete graph} we proceed by considering the following Hamiltonians, with $\gamma$ in front of the Laplacian. This ensures that the time-dependent probability distribution is somewhat compatible with the time-independent one, and does not require to re-evaluate the optimal $\gamma$ for the time-independent approach. Nevertheless the two approaches can be considered equivalent. The Hamiltonians are given by
    \begin{equation}
      H = \gamma L-\ket{w}\bra{w}\hspace{45pt}\mbox{(independent)}
    \end{equation}
    \vspace{-0.5cm}
    \begin{equation}
      H = (1-s)\gamma L - s\ket{w}\bra{w}\hspace{20pt}\mbox{(dependent)}
    \end{equation}\\


    \noindent
    Having defined the hamiltonians, we proceed as in the previous section, following however a more qualitative approach. In order to do so we compare the probability distribution using the heatmap plots introduced in \Cref{subsec:time_independent_benchmarks, subsec:time_dependent_results}.


    \subsection{Probability distribution and qualitative robustness}
    Recalling that for the time-independent quantum walks implementation the optimal $\gamma$ is given by $\gamma=1/N$, we evaluate the probability for $\gamma$ in a neighbourhood of $N$ and up to $T=N$. This allows us to have a complete picture of the probability distribution, as can be seen in the following heatmap plots.

    \input{Chapters/plotscode/plot17}
    As previously discussed we are able to solve search problem with the time-independent algorithm in a time of the order of $T=\pi/2\sqrt{N}$. Indeed we see from the figure above that the probability is close to $p=1$ for $T=11$, as expected. On the other hand the time-dependent approach is able to solve the search with a single iteration for $T\rightarrow N$, showing no significant speedup compared to the classical search. This however leaves space for a multiple run search as introduce in \Cref{subsec:multiple_runs}. We therefore investigate this possibility by evaluating the maximum probability found for $T=\pi/2\sqrt{N}$ with the time-dependent algorithm and study the \textbf{iterations} distribution.

    \input{Chapters/plotscode/plot18}

    It is clear from the plot that the number of run iterations increases with the graph size linearly, although very slowly (notice that $N$ goes up to 101). In the limit for large $N$ the multiple runs search does not improve the time-dependent approach, therefore the standard quantum walks search remains the strongest option.
    \\


    \noindent
    However, we can now address the \textbf{robustness} properties of the two approaches. Similarly to the cycle graph the complete graph has a probability distribution consisting in peaks and valleys when considering the time-independent Hamiltonian. Compared to the smooth probability distribution of the time-dependent algorithm we can safely say that the latter is more robust than the first, both for noise on $T$ and $\gamma$. It is to be noted however that for the cycle graph the time-independent and time-dependent approaches are of comparable performance, therefore the robustness - and the localization as well - \red{improve significantly the time-dependent one}. In this scenario the time-independent approach is much superior in terms of probability, and having less robustness does not justify the \textit{almost} linear time-scaling of the time-dependent one. \\


    \noindent
    Although the time-dependent algorithm is not able to perform as well as the time-independent one, striking is the difference in probability distribution between the Roland-Cerf $s_{RC}(t)$ and the linear $s_L(t)$ interpolating schedules, showing how important is the shape of the interpolating schedule. From the following plot we can see that the time-dependent hamiltonian with the linear interpolating schedule $s_L(t)$ is not able to solve the search for $T=N$. The improvement on the performance is therefore achieved by findind the optimal interpolating schedule; indeed our $s_{RC}(t)$ is similar to the optimal interpolating schedule of Roland and Cerf for the complete graph.

    \input{Chapters/plotscode/plot19}
